Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-18 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Maps for different wind exposure categories

```{r echo = FALSE}
# Code for this map here
```

>>>>

```{r echo = FALSE}
#TS winds and above
TS_wind_exposure <- county_wind(counties = my_fips,
                             start_year = 1988,
                             end_year = 2011,
                             wind_limit = 18,
                             wind_var = "max_sust")
#HU exposures (32.1 mps and above)
HU_wind_exposure <- county_wind(counties = my_fips,
                                start_year = 1988,
                                end_year = 2011,
                                wind_limit = 32.1,
                                wind_var = "max_sust")
TS_wind_2000 <- TS_wind_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) # Max is 1 for hits for top Storm-County
                                                                       # pairs
test <- TS_wind_exposure %>%         
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) %>%
        arrange(desc(count)) %>%
        slice (1:2000) #This gives a max of 17 for number of counts for the top 2000 counties
HU_wind_2000 <- HU_wind_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) # Max of 1 again for hits for top Storm-
                                                                       # County pairs
TS_wind_2000$value <- cut(TS_wind_2000$count, c(0, 1, 2, 3, 4, 5, 6, 7), 
                   labels = c("1", "2", "3", "4", "5", "6", "7"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(7, name = "YlGnBu")
map_TS_2000 <- CountyChoropleth$new(TS_wind_2000)
map_TS_2000$set_zoom(eastern_states)
map_TS_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_TS_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor TS Wind Metric"
a <- map_TS_2000$render()
HU_wind_2000$value <- cut(HU_wind_2000$count, c(0, 1, 2, 3, 4, 5, 6, 7), 
                   labels = c("1", "2", "3", "4", "5", "6", "7"), 
                   include.lowest = TRUE)
map_HU_2000 <- CountyChoropleth$new(HU_wind_2000)
map_HU_2000$set_zoom(eastern_states)
map_HU_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_HU_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor HU Wind Metric"
b <- map_HU_2000$render()
```

```{r}
#Category 3 and above 
cat3_exposure <- county_wind(counties = my_fips,
                                start_year = 1988,
                                end_year = 2011,
                                wind_limit = 50,
                                wind_var = "max_sust")
cat3_2000 <- cat3_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
cat3_2000$value <- cut(cat3_2000$count, c(0, 1, 2, 3, 4, 5, 6, 7), 
                   labels = c("1", "2", "3", "4", "5", "6", "7"), 
                   include.lowest = TRUE)
map_cat3_2000 <- CountyChoropleth$new(cat3_2000)
map_cat3_2000$set_zoom(eastern_states)
map_cat3_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_cat3_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Category 3 and Above Wind Metric"
c <- map_cat3_2000$render()
```

```{r fig.width = 6, fig.height = 8, echo = FALSE}
grid.arrange(a, b, c, ncol = 1)
```

JMF-- I do not think that using the top 2000 Storm-County pairs will be too descriptive (All 3 maps have the identical 2000 pairs), any ideas?
